### 2024-03-01 sections/0intro.tex

\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology. Similar to the first section this will mostly be a recap of useful results developed by AFT. Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}. For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input. Factorization homology will then return an invariant of a manifold; or, depending on one's point of view, an invariant of the input algebra. We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction. More generally, this underpins the theory because it codifies the property of $\otimes$-excision. Finally, we will also state a well-known classification result, due to AFT, about a certain type of disk algebras with stratified structure.

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as prove the following additivity result for locally constant factorization algebras on product spaces:
\begin{theorem*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. Then there is an equivalence
    \[
        \lcfa_{M \times N}(\catC) \simeq \lcfa_{M}(\lcfa_{N}(\catC))
    \]
    between the $\infty$-category of constructible factorization algebras on $M\times N$ and that of those on $M$ valued constructible factorization algebras on $N$.
\end{theorem*}
This result was conjectured by Ginot in \cite{ginot2015} and Ayala [private communication].

Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work. As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure. Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
%
\begin{itemize}
    \item Does there exist a version of factorization algebras that capture information both about the stratified structure of a manifold and about its tangential structure? An even more general, \emph{geometric} version was studied by Pe\~{n}a in \cite{pena2022geometric}. Extending our results and previous known results to such a setting remains desirable.
\end{itemize}
%
In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group. In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
%
\begin{itemize}
    \item Is there a suitable way to encompass this notion in the formalism presented here?
\end{itemize}

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen equivalences in appropriate ways. In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between topological multicategories and their $\infty$-operadic nerve.

>>>>

\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology. Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka. Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}. For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input. Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra. We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction. More generally, this underpins the theory because it codifies the property of $\otimes$-excision. Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition}
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work. As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure. Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
%
\begin{itemize}
    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
\end{itemize}
%
The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept. In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group. In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
%
\begin{itemize}
    \item Is there a suitable way to encompass this notion in the formalism presented here?
\end{itemize}
%
The beginnings of examining this idea can already be found in the thesis \cite{murray2020}, however the development there, while important, is still preliminary.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen-equivalences in appropriate ways. The interested reader can find accounts of these matters in e.g. ..... In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.

### 2024-03-01 sections/2homology.tex

Factorization homology (also topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent.
\end{remark}

@@

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

>>>>

Factorization homology (also topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds. We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.

@@

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors of \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

### 2024-03-01 sections/3algebras.tex

\begin{remark}\label{rem:op_to_op}
    There is an obvious embedding functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
\end{remark}

@@

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss sheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
    %
    \begin{equation}
        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
    \end{equation}
    %
    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
\end{definition}

@@

\begin{remark}
    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases:
    %
    \begin{enumerate}
        \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
        \item For $\hoint$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$ and
        \item Similarly, for $[-1,1]$ the convenient $\infty$-category of basics is again $\bstr = \mathsf{D}_1^{\partial, *}$.
    \end{enumerate}
    %
    We can see that even though factorization algebras, as we have defined them here, don't detect the tangential structure of the manifold, it is usually favorable, if possible, to give the manifold some structure anyway. In particular, the rigid structure of framing is very useful because it massively reduces the spaces of allowed open embeddings.
\end{remark}

@@

\begin{remark}
    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented in \cite{lurie_ha} is independent. 
\end{remark}

>>>>

\begin{remark}\label{rem:op_to_op}
    There is an obvious inclusion functor from the poset $\opens[r](X)$ of open subsets of $X$, ordered by inclusion, to the multicategory $\opens[s](X)$, namely, the one which hits only those multi-morphisms $\{U_i\}_{i \in I} \rightarrow U$, where the cardinality of the finite set $I$ is 1.
\end{remark}

@@

\begin{definition}
    The $\infty$-category of locally constant Weiss cosheaves on a stratified manifold $M$ (or, equivalently, on $\mfld[r]_{/M}$) is the full $\infty$-subcategory
    %
    \begin{equation}
        \csheaves[W, lc]_M (\catC) \subset \csheaves[W]_M (\catC),
    \end{equation}
    %
    of those Weiss cosheaves whose underlying functor $F: \bsc_{/M} \xrightarrow{} \catC$ satisfies
    %
    \begin{equation}
        f(U) \simeq f(V) \Rightarrow F(U) \simeq F(V),
    \end{equation}
    %
    for all $U, V \in \bsc_{/M}$, where $f: \bsc_{/M} \xrightarrow{} \bsc$ denotes the forgetful functor.
\end{definition}

@@

\begin{remark}
    Another perspective on why all of these constructions look the way they do is provided by \cref{lem:disk/M_to_disk}. It applies in all of the above cases, namely:
    %
    \begin{enumerate}
        \item For $\mathbb{R}$, the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^*$,
        \item For $[-1,1]$ the convenient $\infty$-category of basics is $\bstr = \mathsf{D}_1^{\partial, *}$.
        \item For $\hoint$, we could define a convenient $\infty$-category of basics which describes framed 1-dimensional manifolds which only have a right boundary (a concept that we can state because of the framing).
    \end{enumerate}
    %
    We can see that even though factorization algebras, as we have defined them here, don't detect the tangential structure of the manifold, it is usually favorable, if possible, to give the manifold some structure anyway. In particular, the rigid structure of framing is very useful because it massively reduces the spaces of allowed open embeddings.
\end{remark}

@@

\begin{remark}
    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent. 
\end{remark}

### 2024-03-01 sections/4gluing.tex

@@

    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$. That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms. Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting. In the rest of the calculations we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}. Namely, these provide equivalences of functors
    %
    \begin{equation}
        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
    \end{equation}
    %
    which is exactly the collar-gluing property at the level of morphisms.
\end{proof}

@@

@@

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of Dunn additivity \cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}

>>>>

\begin{corollary}\label{cor:fbar_func_discrete}
    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    that is an algebra.
\end{corollary}

@@

    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$. That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms. Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting. In the rest of the calculations we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}. Namely, these provide equivalences of functors
    %
    \begin{equation}
        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
    \end{equation}
    %
    which is exactly the collar-gluing property extended to the level of morphisms.
\end{proof}

@@

Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.

\begin{corollary}\label{cor:gluing_falgs}
    A collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$ induces an equivalence of $\infty$-categories
    %
    \begin{equation}
        \falg_M (\catC) \simeq \falg_{M_-} (\catC) \bigtimes_{\falg_{M_0 \times \mathbb{R}} (\catC)} \falg_{M_+}(\catC).
    \end{equation}
\end{corollary}

@@

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}
